### 2023-03-16 chapter0/chapter0.tex
Tweaked wording to remove phrase "structured domains" as it was not formally introduced yet

In the following years, as the complete genomes of several scientifically important model organisms such as \textit{S. cerevisiae} (baker's yeast), \textit{C. elegans} (roundworm), and \textit{D. melanogaster} (fruit fly) were sequenced for the first time, researchers applied computational methods for predicting disorder to the proteins inferred from their genomes. They discovered that disorder is ubiquitous in eukaryotic\footnote{All life belongs to one of three categories, or domains. Two, Archaea and Bacteria, are all single-celled organisms with simple cellular structures. In contrast, the cells of members of Eukarya, \textit{i.e.} eukaryotes, are complex and contain substructures called organelles, among other differences. All animals, plants, and fungi are eukaryotes, though the domain includes many microorganisms as well.} organisms, with estimates of the fraction of proteins containing disordered segments of greater than 30 residues\footnote{The amino acids that compose the links of a protein chain are conventionally called residues to distinguish them from their related, but chemically distinct, free forms.} ranging between 28 and 63\%~\cite{Dunker2000, Ward2004}. For reference, though the lengths of proteins can vary dramatically, a ``typical'' protein contains on the order of a few hundred residues, so these regions can compose a significant fraction of a protein's length. Because these segments were disordered in their native state, \textit{i.e.} under normal operating conditions, such segments were termed ``intrinsically disordered regions'' (IDRs) to emphasize the disorder was not induced by exposure to chemicals or heat. Furthermore, while most proteins were predicted to contain a mixture of structured domains and IDRs, some ``intrinsically disordered proteins'' (IDPs) were entirely or almost entirely disordered. Thus, disorder was recognized as a pervasive but poorly understood feature of proteins.

>>>>

In the following years, as the complete genomes of several scientifically important model organisms such as \textit{S. cerevisiae} (baker's yeast), \textit{C. elegans} (roundworm), and \textit{D. melanogaster} (fruit fly) were sequenced for the first time, researchers applied computational methods for predicting disorder to the proteins inferred from their genomes. They discovered that disorder is ubiquitous in eukaryotic\footnote{All life belongs to one of three categories, or domains. Two, Archaea and Bacteria, are all single-celled organisms with simple cellular structures. In contrast, the cells of members of Eukarya, \textit{i.e.} eukaryotes, are complex and contain substructures called organelles, among other differences. All animals, plants, and fungi are eukaryotes, though the domain includes many microorganisms as well.} organisms, with estimates of the fraction of proteins containing disordered segments of greater than 30 residues\footnote{The amino acids that compose the links of a protein chain are conventionally called residues to distinguish them from their related, but chemically distinct, free forms.} ranging between 28 and 63\%~\cite{Dunker2000, Ward2004}. For reference, though the lengths of proteins can vary dramatically, a ``typical'' protein contains on the order of a few hundred residues, so these regions can compose a significant fraction of a protein's length. Because these segments were disordered in their native state, \textit{i.e.} under normal operating conditions, such segments were termed ``intrinsically disordered regions'' (IDRs) to emphasize the disorder was not induced by exposure to chemicals or heat. Furthermore, while most proteins were predicted to contain a mixture of structure and disorder, some ``intrinsically disordered proteins'' (IDPs) were entirely or almost entirely disordered. Thus, disorder was recognized as a pervasive but poorly understood feature of proteins.
